Creating line plot of balanced accuracies

### 2020-05-08 Scripts_for_results/02_creating_lineplot_of_balanced_accuracies.Rmd
edits

@@

>>>>

ggplot(all_rfperfs_ba, aes(x=Resolution, y=Performance, color=Resampling, group=Resampling)) +
  geom_line(size=2, position=position_dodge(0.5))+
  geom_point(size=5, position=position_dodge(0.5))+
  geom_errorbar(aes(ymin=Performance-PerformanceSD, ymax=Performance+PerformanceSD), width=1,
                position=position_dodge(0.5)) +
  facet_grid(. ~ Predictor)+
  theme_minimal() +
  theme_bw()+
  xlab("Resolution") + 
  ylab("Balanced Accuracy") + #ylim(-.1,.5) +
  scale_color_discrete(name="Resampling\nTechnique")+
  guides(shape=FALSE, linetype=FALSE)+
  theme(axis.text.x = element_text(size=15,
                                   angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1
  ),
  axis.text.y = element_text(size = 15),
  axis.title.x = element_text(size = 20),
  axis.title.y = element_text(size = 20),
  strip.text.x = element_text(size = 15),
  strip.text.y = element_text(size = 15),
  panel.spacing = unit(2, "lines"),
  legend.text=element_text(size=15),
  legend.title=element_text(size=20),
  plot.title = element_text(size=20),
  legend.position="bottom")

@@

ggplot(all_rfperfs_ba, aes(x=Resolution, y=Performance, color=Resampling, group=Resampling)) +
    geom_line(size=2, position=position_dodge(0.5))+
    geom_point(size=5, position=position_dodge(0.5))+
    geom_errorbar(aes(ymin=Performance-PerformanceSD, ymax=Performance+PerformanceSD), width=1,
                  position=position_dodge(0.5)) +
    facet_grid(. ~ Predictor)+
    theme_minimal() +
    theme_bw()+
    xlab("Resolution") + 
    ylab("Balanced Accuracy") + #ylim(-.1,.5) +
    scale_color_discrete(name="Resampling\nTechnique")+
    guides(shape=FALSE, linetype=FALSE)+
    theme(axis.text.x = element_text(size=15,
                                     angle = 45, 
                                     #margin = ggplot2::margin(t = 35),
                                     hjust = 1
    ),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    strip.text.x = element_text(size = 15),
    strip.text.y = element_text(size = 15),
    panel.spacing = unit(2, "lines"),
    legend.text=element_text(size=15),
    legend.title=element_text(size=20),
    plot.title = element_text(size=20),
    legend.position="bottom")
```
